FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-16 paper.tex
sec headers for viz, gpu

% If using Emacs, put cursor on last closing paren and call "eval-last-sexp" (usually `C-x C-e') to regenerate
\iffalse
(save-excursion
  (let* ((toc (funcall imenu-create-index-function))
         (headers (mapcar (pcase-lambda (`(,str . ,loc)) str)
                          toc)))
    (beginning-of-buffer)
    (search-forward (concat "%% " "--- autogenerated TOC ---"))
    (next-line)
    (beginning-of-line)
    (let ((start (point)))
      (search-forward (concat "%% " "--- end autogenerated TOC ---"))
      (beginning-of-line)
      (delete-region start (point))
      (goto-char start))
    (cl-loop for header in headers
             do (insert (format "%% %s\n" header)))
    (next-line)))
\fi

@@

We introduce \FlowFPX{}, a toolkit for debugging
\fp{} exceptions in an easy and intuitive way~(\cref{s:flowfpx}):
\begin{itemize}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that uses
    Julia's operator overloading to selectively monitor for exceptions and to
    fuzz code for vulnerabilities.
  \item
    To visualize results, \FT{} adapts coalesced stack-trace graphs 
    (CSTGs)~\cite{hmbdrg-cse-2014} for a whole-program view on the generation,
    propagation, and death of exceptional values.
  \item \GPUFPX{}~[CITE] provides fine-grained insights for GPU kernels.
\end{itemize}
%
Together, the \FlowFPX{} tools have helped debug exceptions in a variety
of applications: from ocean simulations to heat models~(\cref{s:casestudies}).
That said, there is much more to explore.
\FlowFPX{} is a growing project and we welcome feedback from domain experts
on how to best suit their workflow.

@@

FILL intro

@@

\subsection{Catching a \NaN{} Killer}

@@

\subsection{\NaN{} propagation monitoring}

@@

\subsection{\NaN{} injection}

@@

>>>>

% If using Emacs, put cursor on last closing paren and call "eval-last-sexp" (usually `C-x C-e') to regenerate
%\iffalse
%(save-excursion
%  (let* ((toc (funcall imenu-create-index-function))
%         (headers (mapcar (pcase-lambda (`(,str . ,loc)) str)
%                          toc)))
%    (beginning-of-buffer)
%    (search-forward (concat "%% " "--- autogenerated TOC ---"))
%    (next-line)
%    (beginning-of-line)
%    (let ((start (point)))
%      (search-forward (concat "%% " "--- end autogenerated TOC ---"))
%      (beginning-of-line)
%      (delete-region start (point))
%      (goto-char start))
%    (cl-loop for header in headers
%             do (insert (format "%% %s\n" header)))
%    (next-line)))
%\fi

@@

We introduce \FlowFPX{}, a toolkit for debugging
\fp{} exceptions in an easy and intuitive way~(\cref{s:flowfpx}):
\begin{itemize}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that uses
    Julia's operator overloading to selectively monitor for exceptions and to
    fuzz code for vulnerabilities.
  \item
    To visualize results, \FT{} adapts coalesced stack-trace graphs 
    (CSTGs, or \CSTG{}s)~\cite{hmbdrg-cse-2014} for a whole-program view on the generation,
    propagation, and death of exceptional values.
  \item \GPUFPX{}~[CITE] provides fine-grained insights for GPU kernels.
\end{itemize}
%
Together, the \FlowFPX{} tools have helped debug exceptions in a variety
of applications: from ocean simulations to heat models~(\cref{s:casestudies}).
That said, there is much more to explore.
\FlowFPX{} is a growing project and we welcome feedback from domain experts
on how to best suit their workflow.

@@

FILL intro: float tracker, viz tools, gpu

@@

\subsubsection{Catching a \NaN{} Killer}

@@

\subsubsection{\NaN{} propagation monitoring}

@@

\subsubsection{\NaN{} injection}

@@

\subsection{Visualization}
\label{s:cstg}

FILL cstg output, how to read, float tracker interface,

\subsection{\GPUFPX{}}
\label{s:gpufpx}

FILL basic idea, loose coupling, typical overhead,
